The main directory contains two important files
\begin{enumerate}
\item arch.in: the architecture file which contains configuration settings for 
      all the sf2s packages.
\item Makefile: the Makefile for all the packages of sf2s. This should not be
      modified unless new files are added and you know what you are doing.
\end{enumerate}
The code is broken up into independent directories
\begin{enumerate}
\item arch: contains sample architecture files for computers that have run
      Sturb.
\item decomp: contains files related to creation and usage of an MPI domain
      decomposition.
\item dns: contains files for the DNS solver Sturb.x.
\item doc: contains documentation for the sf2s package.
\item grid: contains files for the grid generation program grid.x.
\item include: contains the module files which define necessary variables for
      the different subprograms.
\item interp: contains files for the interpolation program interpX1.x,
      interpX2.x, interpX3.x.
\item mgMK: contains files for the multigrid pressure solver.
\item mgMK/test: contains files for the pressure solver test program ptest.x.
\item post: contains files for post-processing simulations using Sturb.x.
\item runfiles: contains sample runfiles for the pressure test program and the 
      DNS solver. Parallel and Serial versions are available.
\item scripts: contains useful scripts for ??? KYLE?
\item serialdev: a directory for new serial files. ??? IS THIS NECESSARY KYLE?
\item utils: contains files that are useful for general tasks.

There is an exhaustive list of all subroutines by directory in
Appendix \ref{app:allsubs}.
\end{enumerate}
